---
title:"Elementary data manipulations"
output: html_document
---

Pick rows: filter()

Pick columns: select()

Sort rows: arrange()

Count things: count()

Make new columns: mutate()

```{r}
install.packages("palmerpenguins")
library(palmerpenguins)
data(package = "palmerpenguins")
```

%>% is pronounced "and then"

# The pipe %>% feeds data into functions

```{r}
head(penguins)
```

```{r}
# head(penguins)
penguins %>%
  head()
```

# The pipe %>% feeds data into functions

```{r}
ggplot(penguins, aes(bill_length_mm, bill_depth_mm, color = species)) +
  geom_point()

penguins |>
  ggplot(aes(bill_length_mm, bill_depth_mm, color = species)) +
  geom_point()
```

# Which to use? Native pipe or old-school pipe?
|> is the future. If you can, use it.

%>% works on older installations. It's the safe choice for now.

We use %>% here because many people still run R 3.x or 4.0.
```{r}

penguins %>%
  filter(species == "Gentoo")
```
# Pick columns species, island, and sex
```{r}

penguins %>%
  select(species, island, sex)
```
# Sort the rows in a table: arrange()
```{r}

penguins %>%
  arrange(desc(bill_length_mm))
```
# Count things
```{r}

penguins
```

```{r}

penguins %>%
  count(species)
```

```{r}

penguins %>%
  count(species, island)
```

# Use the pipe to build analysis pipelines

```{r}

penguins %>%
  filter(species == "Adelie")
```
Use the pipe to build analysis pipelines
```{r}

penguins %>%
  filter(species == "Adelie") %>%
  select(island, sex) %>%
  count(island, sex)
```
# Make a new table column: mutate()
Example: flipper length in cm
```{r}

penguins %>%
  select(species, island, flipper_length_mm)
```
```{r}

penguins %>%
  select(species, island, flipper_length_mm) %>%
  mutate(flipper_length_cm = flipper_length_mm / 10)
```

Make multiple columns at once
```{r}

penguins %>%
  select(species, island, flipper_length_mm) %>%
  mutate(
    flipper_length_cm = flipper_length_mm / 10, # <- notice the comma
    flipper_length_in = flipper_length_mm / 25.4
  )
# https://wilkelab.org/SDS375/slides/data-wrangling-1.html#40
```
